%---------------------------------------------------
% LaTeX Resume
% Template Author:  Jake Gutierrez
% Adapted from:     https://github.com/sb2nov/resume
% License:          MIT
%---------------------------------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1


%---------CUSTOM COMMANDS--------
\newcommand{\resumeItem}[1]{
\item\small{
        {#1 \vspace{-2pt}}
    }
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        {\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-----------RESUME CONTENT-----------
\begin{document}


%--------------HEADING---------------
\begin{center}
	\textbf{\Huge Rajit Banerjee} \\ \vspace{5pt}
	\href{https://rajitbanerjee.com}{\small rajitbanerjee\textbf{.com}} $|$
	\href{https://linkedin.com/in/rajitbanerjee/}{\small \textbf{linkedin}: rajitbanerjee} $|$
	\href{https://github.com/rajitbanerjee}{\small \textbf{github}: rajitbanerjee} $|$
	\href{mailto:rajit.banerjee@ucdconnect.ie}{\small rajit.banerjee\textbf{@}ucdconnect\textbf{.ie}} $|$
	{\small \textbf{Dublin}, Ireland}
\end{center}

% Alternate Heading:
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{https://rajitbanerjee.com/}{\Large Rajit Banerjee}} & Email : \href{mailto:rajit.banerjee@ucdconnect.ie}{rajit.banerjee@ucdconnect.ie}\\
%   \href{https://rajitbanerjee.com}{https://rajitbanerjee.com} & Mobile : +353 XXXXXXXXX \\
% \end{tabular*}


%--------------EDUCATION--------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University College Dublin}{Dublin, Ireland}
{\textbf{BSc (Hons.) Computer Science with Data Science}}{Sep. 2018 -- Jun. 2022 (Expected)}

\resumeItemListStart
\resumeItem{\textbf{GPA}: 4.11/4.20 (First Class Honours)}
\resumeItem{\textbf{Coursework}:
	Data Structures, Algorithms,
	Introduction to AI,
	Programming for Big Data,
	Databases \& Information Systems,
	Business Analytics,
	Software Engineering I \& II,
	Linear Algebra II,
	Social Entrepreneurship}

\resumeItem{\textbf{Honours and Awards}:
	\href{https://www.ucd.ie/adastraacademy/academic/}{UCD Ad Astra Academic Scholarship},
	\href{https://www.ucd.ie/global/scholarships/}{UCD Global Undergraduate Scholarship},
	BSc Computer Science Scholarship
	(\href{https://sisweb.ucd.ie/usis/W_HU_REPORTING.P_DISPLAY_QUERY?p_query=SC101-1A&p_parameters=A8A08F4E214445171B5771A1009E1D5B2E8D2BA93239FA8867648F2551D1F6E74111E7B3FBB422649785AC454612F967929BC94109BC9FA35BEAD1F53D23BA161359586343D3237CFDBE22184AE066F37B92C3B3C7382336AC2A2EAE5A092F63FC7A402CF2646B9597CDAAB378E40E1B}{Stage 2},
	\href{https://sisweb.ucd.ie/usis/W_HU_REPORTING.P_DISPLAY_QUERY?p_query=SC101-1A&p_parameters=A8A08F4E214445171B5771A1009E1D5B2E8D2BA93239FA8867648F2551D1F6E74111E7B3FBB422649785AC454612F96787A57507118273967D6FD3CA5758624C79D7843C965FDFB69E23ABD0A5BF3B8352A54C50CBC563B72C4800831552834F550B235F0EFC644A6070F3328CE618D803B3E3CD94D6ADF3C463A5184F86FFAB}{Stage 3}),
	Insight Centre Research Scholarship,
	UCD Embark Award}
\resumeItemListEnd

\resumeSubHeadingListEnd


%---------------SKILLS------------------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
	      \textbf{Languages}{: Python, Java, Go, SQL (MySQL, BigQuery), HTML/CSS, C, Scheme (Racket), R} \\
	      \textbf{Tools}{: Git, Docker, Agile (Scrum, Kanban), Linux/Shell, MS Excel, Tableau, Vim, VS Code, IntelliJ IDEA} \\
	      }}

	      \small{\item{
	      \textbf{Certificates}{:
		      \underline{Virtual Internships}
		      (\href{https://insidesherpa.s3.amazonaws.com/completion-certificates/KPMG/m7W4GMqeT3bh9Nb2c_KPMG_oXfzxXCwznR6kbwCr_completion_certificate.pdf}{KPMG (Data Analytics)},
		      \href{https://insidesherpa.s3.amazonaws.com/completion-certificates/JP\%20Morgan/R5iK7HMxJGBgaSbvk_JPMorgan\%20Chase_oXfzxXCwznR6kbwCr_completion_certificate.pdf}{JPMorgan Chase \& Co. (Software Engineering)}),
		      \newline
		      \underline{Kaggle}
		      (\href{https://www.kaggle.com/learn/certification/rajitbanerjee/advanced-sql}{Advanced SQL},
		      \href{https://www.kaggle.com/learn/certification/rajitbanerjee/intro-to-machine-learning}{Intro to Machine Learning},
		      \href{https://www.kaggle.com/learn/certification/rajitbanerjee/data-visualization}{Data Visualization}),
		      \underline{HackerRank}
		      (\href{https://www.hackerrank.com/certificates/0a172d60bd75}{Rest API},
		      \href{https://www.hackerrank.com/certificates/451957828c61}{Python},
		      \href{https://www.hackerrank.com/certificates/753d7e1f1e95}{Java})
	      } \\
	      }}
\end{itemize}


%------------WORK EXPERIENCE-------------
\section{Work Experience}
\resumeSubHeadingListStart

\resumeSubheading
{\href{https://www.insight-centre.org/}{Insight SFI Research Centre for Data Analytics}}{Dublin, Ireland}
{\textbf{Research Intern} $|$ \emph{Python, OpenCV, Docker, Bash}}{Jun. -- Aug. 2020}
\resumeItemListStart
\resumeItem{Project (human body pose estimation): Performed experiments with multiple pose estimation models to
	estimate the body keypoints of novice athletes (runners) using pre-recorded input videos.}
\resumeItem{Designed Bash scripts and Docker containers to automate video processing on a remote server.}
\resumeItem{Analysed time-series data and computed a variety of body pose angles from video frames to assist runners with maintaining optimal form and posture.}
\resumeItemListEnd


\resumeSubheading
{\href{https://www.prmfincon.com/}{PRM Fincon Services Pvt. Ltd.}}{Kolkata, India}
{\textbf{Python Development Intern} $|$ \emph{Python, OpenCV, Tesseract OCR, Camelot}}{Jun. -- Aug. 2019}
\resumeItemListStart
\resumeItem{Project (data extraction from financial reports): Refactored and optimised code to extract tabular data (balance sheets, income statements) by applying various image processing techniques to PDF pages.}
\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\href{https://github.com/rajitbanerjee/scripts}{\textbf{Scripts} $|$
		\emph{Python, Bash}}}{Jul. 2020 -- Present}
\resumeItemListStart
\resumeItem{A collection of Bash and Python scripts to simplify a variety of day-to-day tasks, including merging, encrypting, modifying PDFs; quick installations for utilities; shortcuts for common terminal commands, and so on.}
\resumeItemListEnd

\resumeProjectHeading
{\href{https://github.com/rajitbanerjee/Scrabble}{\textbf{Scrabble} $|$
		\emph{Java, JavaFX, JUnit, Scrum}}}{Jan. -- May 2020}
\resumeItemListStart
\resumeItem{Designed the game logic, GUI and bot, in a team of 3, using Java , JavaFX (GUI) and JUnit (testing).}
\resumeItem{Followed Agile (Scrum) methodology, acting as the Scrum Master for multiple sprints.}
\resumeItemListEnd

\resumeProjectHeading
{\href{https://drive.google.com/file/d/1uwZpb3X_Qh47Q82x8_q9oTO0uWI-9oEP/view}{\textbf{Investment Portfolio Optimisation} $|$
		\emph{Microsoft Excel}}}{Mar. -- Apr. 2020}
\resumeItemListStart
\resumeItem{Modelled the stock price behaviour of 8 companies and optimised a two-week investment strategy with
	82\% accuracy, using integer linear programming, regression and volume risk analysis.}
\resumeItemListEnd


\resumeSubHeadingListEnd


%------------EXTRACURRICULAR----------------
\section{Extracurricular}
\resumeSubHeadingListStart

\resumeItemListStart
\resumeItem{\textbf{Student Ambassador}: UCD spokesperson, representative and point of contact for prospective students.}
\resumeItem{\textbf{Class Representative}: elected representative to the UCD Students’ Union for Computer Science students.}
\resumeItem{\textbf{Computer Science Peer Mentor}: advisor to 10 first-year Computer Science students.}
\resumeItem{\textbf{CS Sparks}: coding workshop facilitator for students from DEIS schools in their Transition Year.}
\resumeItem{\textbf{Photography}: keen interest in nature, street and event photography; active member of Photography Club.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
